% Adapted from https://github.com/gboeing/cv

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) so accented characters are a single glyph
\usepackage[utf8]{inputenc} % allow input of utf-8 encoded characters
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % automatically regionalize hyphens, quote marks, etc
\usepackage{microtype} % improves text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto} % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts

% what is your name?
\newcommand{\myname}{Niklas Hlubek}

% define a default font face and set it as the body font
\usepackage{crimson} % document's serif font
\usepackage{helvet}  % document's sans serif font

% define how far to tab for list items with left-aligned date - different font faces need different widths
\newcommand{\listtabwidth}{1.75cm}

% set name font to title the document
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*}{20}
\titleformat{\section}{\sffamily\small\bfseries\lsstyle\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{24pt plus 4pt minus 2pt}{12pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{12pt plus 4pt minus 2pt}{8pt plus 2pt minus 2pt}

% set page margins
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% define space between list items
\newcommand{\listitemspace}{0.15em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
            \setlength{\parskip}{0em}
            \setlength{\itemsep}{\listitemspace}
            \setlength{\parsep}{\listitemspace}}}
    {\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print the month and year only when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    pdfauthor   = {\myname},
    pdfkeywords = {Social Data Science, Epidemiology, Public Health},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright

    % display name as the document title
    \namefont{\myname}

    % contact info
    \vspace{1em}
    \begin{minipage}[t]{0.64\textwidth}
        Department of Epidemiology \\
        University Medical Center Utrecht, Utrecht University
        \\ Utrecht, the Netherlands
    \end{minipage}
    \begin{minipage}[t]{0.34\textwidth}
        e: \href{mailto:n.hlubek@umcutrecht.nl}{n.hlubek@umcutrecht.nl} \\
        w: \href{https://nhlubek.github.io/}{nhlubek.github.io}
    \end{minipage}
    \vspace{0.5em}

    \section*{Education}

    \begin{tablist}

        \item[PhD.]  \tab Epidemiology, Utrecht University, 2025

        \item[MSc.]  \tab Social Policy and Public Health, Utrecht University, 2022

        \item[MSc.]  \tab Psychological Research, University of Edinburgh, 2021

        \item[BSc.]  \tab Psychology, Erasmus University Rotterdam, 2019

    \end{tablist}

    \section*{Professional}

    \begin{tablist}
    
    	\item[2023-] \tab University Medical Center, Julius Center for Health Sciences \\
						  Doctoral Candidate \\
						  Department of Epidemiology

            \item[2024] \tab ISGlobal Barcelona Institute for Global Health \\
                             Visiting Researcher \\
                             Urban Planning, Environment and Health, Air Pollution
						  
		\item[2022] \tab Mental Health Europe, Policy and Projects Assistant

            \item[2020] \tab University Medical Center Hamburg Eppendorf \\
                            Research Assistant  \\
                            Neuropsychology and Psychotherapy Research Unit \\ Department of Psychiatry and Psychotherapy 
        
            \item[2019-20]  \tab Max Planck Institute for Cognitive and Brain Sciences \\
                          Research Assistant  \\
                          Department of Neurology

    \end{tablist}

    \section*{Research Interests}

    \begin{itemize}

        \item Social Epidemiology.

        \item ?.

    \end{itemize}

    \section*{Publications}
    
    \begin{tablist}
    
    	 \item[2024] \tab \textbf{Hlubek, N.}, Koop Y., Wagtendonk A., Vaartjes I. \enquote{Temporal Trends in Air Pollution Exposure across Socioeconomic Groups in the Netherlands.} \textit{Int. J. Environ. Res. Public Health}. \url{https://doi.org/10.3390/ijerph21080976.}.
	 
    	 \item[2022] \tab \textbf{Hlubek, N.}, Templeton, A., Wiseman-Gregg, K.  \enquote{A social identity approach to COVID-19 transmission in hospital settings.} \textit{Journal of Applied Social Psychology}. \url{https://doi.org/10.1111/jasp.12948}.
	     
    	 \item[2022] \tab Bomke P., \textbf{Hlubek, N.}  \enquote{Entwicklung der Sozialpsychatrie in Europa - die Sicht von Mental Health Europe} \textit{Kerbe - Forum fuer soziale Psuychatrie}.
	    
    	 \item[2021] \tab Moritz S., Xie J., Penney D., Biehl L., \textbf{Hlubek, N.}, Elmers J., Beblo T., Hottenrott B. \enquote{The magnitude of neurocognitive impairment is overestimated in depression: the role of motivation, debilitating momentary influences, and the overreliance on mean differences.} \textit{Psychological Medicine}. \url{https://doi.org/10.1017/S0033291721004785}.

    	 \item[2020] \tab Jelinek L., \textbf{Hlubek, N.}, Moritz S., Miegel F., Voderholzer U. \enquote{Zwangsstörungen während COVID-19: Sind Menschen mit Waschzwängen besonders betroffen.} \textit{z-aktuell}. 
       
    \end{tablist}
    
    \section*{Presentations}
    
    \begin{tablist}
    
    	 \item[2022] \tab Templeton A., \textbf{Hlubek, N.} \enquote{Social identity processes in hospital workers risk perception and adherence to safety guidance during the COVID-19 pandemic.} Paper presented at the \textbf{BPS Social Psychology Section Annual Conference}

         \item[2021] \tab \textbf{Hlubek, N.}, Templeton A. \enquote{A social identity approach to COVID-19 transmissions in hospital settings – Barriers and avenues to safe behaviour in healthcare workers.} Project presented to the \textbf{Scottish Government COVID-19 Nosocomial Review Group}
    
    \end{tablist}

    \section*{Technical Skills}

    \begin{itemize}

        \item \texttt{R} \tab Advanced
        
        \item \texttt{Python} \tab novice
        
    \end{itemize}

    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        %\vspace{6em}
        \vfill
        Updated \monthyeardate\today
    \end{center}

\end{document}